Supplementary Materials And Methods

### 2020-11-10 Supplementary_mat_met.Rmd
entrez_id check
after adding liftover data, update code

```{r,  eval=FALSE}
clearclipfinal <- hg18 %>%
  inner_join(clearclip, by= c("entrezgene"= "gene.id", 
                              "hgnc_symbol"= "gene.symbol")) %>%
  distinct()
```

@@

>>>>

```{r,  eval=FALSE}
clearclipfinal <- hg18 %>%
  inner_join(clearclip, by= c("entrezgene_id"= "gene.id", 
                              "hgnc_symbol"= "gene.symbol")) %>%
  distinct()
```

@@

```
Please note that we have provided the hg18 liftover dataset under the data folder (lift18), since server error may occur.

lift18 <- read_tsv("data/lift18.txt")
